---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rmissingno

<!-- badges: start -->
<!-- badges: end -->

The goal of rmissingno is to emulate some of the interesting missing data exploration tools available in the python package `missingno`. Code is more or less from scratch, all the bad ideas and terrible implementation is mine. API is deeply unstable and likely to change.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mattsq/rmissingno")
```
## Example

I currently (badly) implement two of the methods from the package. 

The first uses `corrplot` to plot the correlations between missing data in various variables in a dataframe:

```{r plot_missing_correl}
library(rmissingno)
library(mice)
data("tbc")

rmissingno::plot_missing_correl(tbc)

```

The second uses hierarchical clustering to find associations between missingness, to draw out more complex patterns than pairwise correlation might hide:

```{r }
rmissingno::plot_missing_hclust(tbc, distance = "euclidean")
```

